% Veri.fi — BUIDL CTC Hackathon Pitch Deck
% LaTeX Beamer | Compiles on Overleaf | No external files

\documentclass[11pt]{beamer}
\usetheme{Madrid}
\usecolortheme{default}
\setbeamertemplate{navigation symbols}{}
\setbeamercolor{structure}{fg=teal!70!black}
\setbeamercolor{palette primary}{bg=teal!20,fg=black}
\setbeamercolor{palette secondary}{bg=teal!30,fg=black}
\setbeamercolor{palette tertiary}{bg=teal!40,fg=black}
\setbeamercolor{frametitle}{bg=teal!25,fg=black}
\setbeamertemplate{itemize items}[circle]
\setbeamertemplate{enumerate items}[default]
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath}

% -----------------------------------------------------------------------------
\title{Veri.fi}
\subtitle{AI-Verified Proof of Action on Creditcoin}
\author{BUIDL CTC Hackathon}
\institute{Build for the Real World}
\date{}
% -----------------------------------------------------------------------------

\begin{document}

% ========== SLIDE 1: Title ==========
\begin{frame}
\titlepage
\vspace{-0.5em}
\begin{center}
\large \textbf{Turn real-world activity into programmable proof.}
\end{center}
\end{frame}

% ========== SLIDE 2: Problem ==========
\begin{frame}{Problem}
Real-world verification is broken:
\begin{itemize}
\item Manual verification is \textbf{expensive} and slow
\item Self-reported proof is \textbf{easy to fake}
\item Centralized systems create \textbf{trust bottlenecks}
\item Reward settlement is \textbf{opaque} and off-chain
\end{itemize}
\vspace{0.5em}
Many economically important activities (infrastructure inspections, delivery confirmation, retail checks, field operations, event attendance) remain hard to verify digitally.
\end{frame}

% ========== SLIDE 3: Solution ==========
\begin{frame}{Solution}
Veri.fi: decentralized verification with on-chain settlement.
\begin{itemize}
\item \textbf{Task creation} — Sponsors define tasks and lock rewards
\item \textbf{Proof submission} — Participants submit evidence (photo, GPS, metadata)
\item \textbf{AI verification} — Backend scores evidence (visual, location, time, anti-fraud)
\item \textbf{Creditcoin settlement} — Smart contract releases reward when verification passes
\end{itemize}
\end{frame}

% ========== SLIDE 4: How It Works ==========
\begin{frame}{How It Works}
\begin{center}
Sponsor creates task \\
$\downarrow$ \\
Participant submits evidence \\
$\downarrow$ \\
AI verifies (score $\geq$ threshold) \\
$\downarrow$ \\
Creditcoin releases reward
\end{center}
\vspace{0.5em}
One flow. Transparent. Programmable.
\end{frame}

% ========== SLIDE 5: Demo Example ==========
\begin{frame}{Demo Example}
\begin{enumerate}
\item User 1 (sponsor) creates a task and locks reward on Creditcoin
\item User 2 (participant) completes the task in the real world
\item User 2 uploads photo proof (and optional GPS)
\item AI verifies the evidence; score is computed
\item Creditcoin releases the reward to User 2
\end{enumerate}
\vspace{0.5em}
Task closes. Proof and payout are on-chain.
\end{frame}

% ========== SLIDE 6: Why Creditcoin ==========
\begin{frame}{Why Creditcoin}
\begin{itemize}
\item \textbf{Escrow} — Rewards held on-chain until verification passes
\item \textbf{Transparent settlement} — Anyone can see when and why rewards are released
\item \textbf{Programmable incentives} — Tasks and thresholds are set by sponsors; protocol executes
\item \textbf{On-chain auditability} — Evidence hash and verification result can be attested
\end{itemize}
\end{frame}

% ========== SLIDE 7: Hackathon Track Fit ==========
\begin{frame}{Hackathon Track Fit}
\textbf{BUIDL CTC — Build for the Real World}
\vspace{0.5em}
\begin{itemize}
\item \textbf{DePIN} — Verify physical infrastructure (EV chargers, telecom nodes, sensors)
\item \textbf{RWA} — Validate physical assets, field inspections, logistics events
\item \textbf{DeFi-adjacent settlement} — Escrow and automated reward release on Creditcoin
\end{itemize}
\vspace{0.5em}
Strong fit for real-world coordination and verification.
\end{frame}

% ========== SLIDE 8: Architecture ==========
\begin{frame}{Architecture}
\begin{itemize}
\item \textbf{Frontend} — Next.js; task creation, proof upload, dashboard
\item \textbf{Verification backend} — API routes; scoring and orchestration
\item \textbf{AI analysis} — Vision (DeepInfra/OpenAI), location and timestamp checks
\item \textbf{Evidence storage} — Supabase (optional); proof images and metadata
\item \textbf{Creditcoin} — VeriActEscrow; escrow and payout on testnet
\end{itemize}
\end{frame}

% ========== SLIDE 9: Use Cases ==========
\begin{frame}{Use Cases}
\begin{itemize}
\item EV charger verification
\item Logistics and delivery confirmation
\item Retail and store audits
\item Field inspections and asset condition
\item Community and event data collection
\end{itemize}
\vspace{0.5em}
Any real-world activity that can be evidenced and scored.
\end{frame}

% ========== SLIDE 10: Closing ==========
\begin{frame}{Closing}
\begin{center}
\Large \textbf{Veri.fi} \\
\large Turn real-world activity into programmable proof. \\
\vspace{1em}
Proof it $\rightarrow$ We verify it $\rightarrow$ You get paid. \\
\vspace{1em}
\textbf{Build for the Real World.}
\end{center}
\end{frame}

\end{document}
